\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\medskip
Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003}, 
\begin{equation} 
   \mathcal{Q} = U_{f} b \lambda_{f}.\label{eqn:guaneqn} 
\end{equation} 
Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150}), respectively. This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on finger's tip velocity).

>>>>

\medskip
Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003},    
\begin{equation}   
   \mathcal{Q} = U_{f} b \lambda_{f}.\label{eqn:guaneqn} 
\end{equation}  
Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively. This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on finger's tip velocity, Table~\ref{table:Heleshaw}).

### 2017-07-04 Papers/ViscousInstabilities/article_table.tex
updates

\begin{landscape}
\begin{table}
  \begin{tabular}{c | c c  c  c  c  c  c  c  c  c   c}
    \hline
      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $\mathbf{K}_{1}$ & $\mathbf{K}_{2}$ & $\mathbf{K}_{3}$ & $\mathbf{K}_{4}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{\circ}_{w}$ \\ 
    \hline
     \ref{section:results_validation} & 0.2 & 1.0 & 0.0 & 1.0 & 2.5 & 1.0 & N/A & N/A & 0.2 & 0.3 & 1.0 \\
     \ref{section:results_homo_hete}(homogenous)  & 0.2 & 10.0 & 0.0 & 1.0 & 1.e-10 & N/A & N/A & N/A & 0.2 & 0.3 & \red{XX}  \\
     \ref{section:results_homo_hete}(heterogenous) & 0.2 & 1.0 & 0.0 & 1.0 & 1.e-11 -- & 1.e-12 -- & 1.e-12 -- & 1.e-10 & 0.2  & 0.3 & 1.0 \\
      &   &  &  &  & 5.e-10 & 5.e-10 & 1.e-10  &  &  &  & \\
     \ref{section:results_hete_fix_adapt}  & 0.2 & 1.0 & 0.0 & 1.0  & 3.0 & 2.0 & 5.0 & 1.0 & 0.2 & 0.3 & \red{XX}  \\
     \ref{section:results_dinlet}  & 0.2 & 1.0 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & 0.2  & 0.3 & \red{XX}  \\
     \hline
   \end{tabular}
   \caption{Sumary of model set-up used in the numerical simulations. Superscript $\circ$ denotes initial condition. $\mathbf{K}_{i}$ is in \red{XX} (units) and $u^{\circ}_{w}$ is in \red{XX} (units). \red{(PLEASE: 1. DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES; 2. \underline{REPLACE ALL \red{XX}}; 3. COMPLETE THE TABLE FOR ALL SECTIONS/SIMULATIONS; 4. UNITS FOR K AND U.)}  $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations. }\label{table:setup}
\end{table}
\end{landscape}
\clearpage

>>>>

%%%
%%%   TABLE 1
%%%
\begin{landscape}
\begin{table}
  \begin{tabular}{c | c c  c  c  c  c  c  c  c  c   c}
    \hline
      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $\mathbf{K}_{1}$ & $\mathbf{K}_{2}$ & $\mathbf{K}_{3}$ & $\mathbf{K}_{4}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{\circ}_{w}$ \\ 
    \hline
     \ref{section:results_validation} & 0.2 & 1.0 & 0.0 & 1.0 & 2.5 & 1.0 & N/A & N/A & 0.2 & 0.3 & 1.0 \\
     \ref{section:results_homo_hete}(homogenous)  & 0.2 & 10.0 & 0.0 & 1.0 & 1.e-10 & N/A & N/A & N/A & 0.2 & 0.3 & \red{XX}  \\
     \ref{section:results_homo_hete}(heterogenous) & 0.2 & 1.0 & 0.0 & 1.0 & 1.e-11 -- & 1.e-12 -- & 1.e-12 -- & 1.e-10 & 0.2  & 0.3 & 1.0 \\
      &   &  &  &  & 5.e-10 & 5.e-10 & 1.e-10  &  &  &  & \\
     \ref{section:results_hete_fix_adapt}  & 0.2 & 1.0 & 0.0 & 1.0  & 3.0 & 2.0 & 5.0 & 1.0 & 0.2 & 0.3 & \red{XX}  \\
     \ref{section:results_dinlet}  & 0.2 & 1.0 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & 0.2  & 0.3 & \red{XX}  \\
     \hline
   \end{tabular}
   \caption{Sumary of model set-up used in the numerical simulations. Superscript $\circ$ denotes initial condition. $\mathbf{K}_{i}$ is in \red{XX} (units) and $u^{\circ}_{w}$ is in \red{XX} (units). \red{(PLEASE: 1. DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES; 2. \underline{REPLACE ALL \red{XX}}; 3. COMPLETE THE TABLE FOR ALL SECTIONS/SIMULATIONS; 4. UNITS FOR K AND U.)}  $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations. }\label{table:setup}
\end{table}
\end{landscape}
\clearpage

%%%
%%%   TABLE 2
%%%
\begin{table}
  \begin{tabular}{c | c c c c}
    \hline\hline
                                  & {\bf K}                                  & {\it VR}  & $\lambda_{f}^{\text{(calc)}}$ (cm) & $\lambda_{f}^{\text{(simul)}}$ (cm) \\
                                  & $\left(\text{cm}^{2}\right)$              &           &  (Eqn.~\ref{eqn:guaneqn})  &                    \\
    \hline\hline
    {\bf Case 1} (homogeneous)    &  1$\times$10$^{-10}$                      &    10      &  0.13-0.75                 &   0.45-0.70       \\
    {\bf Case 2} (homogeneous)    &  1$\times$10$^{-10}$                      &    150     &  0.30-0.75                 &   0.50-0.90       \\
    {\bf Case 3} (heterogeneous)  &  1$\times$10$^{-12}$-5$\times$10$^{-10}$   &    10      &  0.25-4.50                 &   0.44-0.56       \\
    {\bf Case 4} (heterogeneous)  &  1$\times$10$^{-12}$-5$\times$10$^{-10}$   &    150     &  0.88-3.00                 &   0.24-0.40       
  \end{tabular}
   \caption{Flow simulations in Heleshaw cells (Section~\ref{section:results_homo_hete}): summary of finger width calculations using Eqn.~\ref{eqn:guaneqn} and obtained through numerical simualtions. $\lambda_{f}^{\text{calc}}$ was calculated based on fingers' tip velocities and outflow rate. Calculations were based on simulation data obtained from snapshots shown in Fig.~\ref{fig:homoheleshaw_VN10_VN150}.}\label{table:Heleshaw}
\end{table}
